ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT

### 2018-04-21 asce-revision-final.tex
renaming figures 5a, 6a, 7a to 5, 6, 7
revision of figure 2, the corresponding caption, and the surv sign table

\begin{figure}
\includegraphics[width=\textwidth]{fig2}
\caption{Set of prior and posterior cdfs for $\lambda$ for two surprising observations $t_1 = 1$, $t_2 = 2$ (left)
and two unsurprising observations $t_1 = 10$, $t_2 = 11$ (right).}
\label{fig:setofpost-pdc-nopdc}
\end{figure}

@@

\begin{table}
\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout}.}
\label{tab:brake-survsign}
\centering
\begin{tabular}{cccclcccccl}
  \toprule
M & H & C & P & $\Phi$ & \quad & M & H & C & P & $\Phi$\\ 
  \midrule
1 & 0 & 1 & 1 & 0.25 & & 1 & 0 & 2 & 1 & 0.50 \\ 
1 & 0 & 1 & 2 & 0.50 & & 1 & 0 & 2 & 2 & 0.83 \\ 
1 & 0 & 1 & 3 & 0.75 & & 1 & 0 & 3 & 1 & 0.75 \\ 
0 & 1 & 0 & 1 & 0.50 & & 1 & 1 & 0 & 1 & 0.50 \\ 
0 & 1 & 0 & 2 & 0.83 & & 1 & 1 & 0 & 2 & 0.83 \\ 
0 & 1 & 1 & 1 & 0.50 & & 1 & 1 & 1 & 1 & 0.62 \\ 
0 & 1 & 1 & 2 & 0.83 & & 1 & 1 & 1 & 2 & 0.92 \\ 
0 & 1 & 2 & 1 & 0.50 & & 1 & 1 & 2 & 1 & 0.75 \\ 
0 & 1 & 2 & 2 & 0.83 & & 1 & 1 & 2 & 2 & 0.97 \\ 
0 & 1 & 3 & 1 & 0.50 & & 1 & 1 & 3 & 1 & 0.88 \\ 
0 & 1 & 3 & 2 & 0.83 \\
0 & 1 & 4 & 1 & 0.50 \\
0 & 1 & 4 & 2 & 0.83 \\
   \bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig5a}
\caption{Sets of posterior predictive reliability functions for the four component types
for observations in line with prior expectations (case~1).}
\label{fig:comppost-1}
\end{figure}

@@

For the second case, with $t_1^\text{C} = 1$, $t_2^\text{C} = 2$, $t_1^\text{P} = 0.25$, $t_2^\text{P} = 0.5$
and $\tnow = 2$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 2^+$),
we assume to observe surprisingly early failures;
the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-2}.
%
\begin{figure}
\includegraphics[width=\textwidth]{fig6a}
\caption{Sets of posterior predictive reliability functions for the four component types
for surprisingly early failures (case~2).}
\label{fig:comppost-2}
\end{figure}
%
Having observed the system only until $t = 2$, the data are not very informative,
such that prior and posterior predictive reliability bounds are very similar.
For C, the effect of the early failures is however still visible,
and posterior imprecision, i.e., the range between lower and upper posterior bound, is notably larger
as compared to prior imprecision, and substantially larger than posterior imprecision in case~1.
The effect for P is less pronounced,
mainly because observing $\vec{t}^\text{P} = (0.25, 0.5, 2^+, 2^+)$ for P is less extreme
as observing $\vec{t}^\text{C} = (1, 2, 2^+, 2^+)$ for C.

@@

For the third case, we assume to observe surprisingly late failures,
namely $t_1^\text{C} = 11$, $t_2^\text{C} = 12$, $t_1^\text{P} = 8$, $t_2^\text{P} = 9$,
and $\tnow = 12$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 12^+$);
the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-3}.
%
\begin{figure}
\includegraphics[width=\textwidth]{fig7a}
\caption{Sets of posterior predictive reliability functions for the four component types
for surprisingly late failures (case~3).}
\label{fig:comppost-3}
\end{figure}
%
Having observed the system for a much longer time than in case 2,
the data contain now much more information,
resulting in considerable differences between prior and posterior bounds. %predictive reliability
The effect of these surprisingly late failures is most prominent for P,
with a set considerably shifted to the right and having very wide posterior bounds.
The posterior set for C also indicates that,
after having seen these late failures, one expects type C components to fail much later.
This effect is also visible for M and H,
but is weaker for them as there is only one component of each in the system.

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{fig2}
\caption{Set of prior and posterior cdfs for $\lambda$ for (a) two surprising observations $t_1 = 1$, $t_2 = 2$
and (b) two unsurprising observations $t_1 = 10$, $t_2 = 11$.}
\label{fig:setofpost-pdc-nopdc}
\end{figure}

@@

\begin{table}
\caption{Survival signature values $\not\in \{0,1\}$ for the simplified automotive brake system depicted in Figure~\ref{fig:brakesys-layout}.}
\label{tab:brake-survsign}
\centering
\begin{tabular}{cccclcccccl}
  \toprule
M & H & C & P & $\Phi$ \\ 
  \midrule
1 & 1 & 0 & 1 & 0.50 \\
1 & 1 & 0 & 2 & 0.83 \\
1 & 1 & 1 & 1 & 0.62 \\
1 & 1 & 1 & 2 & 0.92 \\
1 & 1 & 2 & 1 & 0.75 \\
1 & 1 & 2 & 2 & 0.97 \\
1 & 1 & 3 & 1 & 0.88 \\
1 & 0 & 1 & 1 & 0.25 \\ 
1 & 0 & 1 & 2 & 0.50 \\ 
1 & 0 & 1 & 3 & 0.75 \\ 
1 & 0 & 2 & 1 & 0.50 \\
1 & 0 & 2 & 2 & 0.83 \\
1 & 0 & 3 & 1 & 0.75 \\
0 & 1 & 0 & 1 & 0.50 \\
0 & 1 & 0 & 2 & 0.83 \\
0 & 1 & 1 & 1 & 0.50 \\
0 & 1 & 1 & 2 & 0.83 \\
0 & 1 & 2 & 1 & 0.50 \\
0 & 1 & 2 & 2 & 0.83 \\
0 & 1 & 3 & 1 & 0.50 \\
0 & 1 & 3 & 2 & 0.83 \\
0 & 1 & 4 & 1 & 0.50 \\
0 & 1 & 4 & 2 & 0.83 \\
   \bottomrule
\end{tabular}
\end{table}

@@

\begin{figure}
\includegraphics[width=\textwidth]{fig5}
\caption{Sets of posterior predictive reliability functions for the four component types
for observations in line with prior expectations (case~1).}
\label{fig:comppost-1}
\end{figure}

@@

For the second case, with $t_1^\text{C} = 1$, $t_2^\text{C} = 2$, $t_1^\text{P} = 0.25$, $t_2^\text{P} = 0.5$
and $\tnow = 2$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 2^+$),
we assume to observe surprisingly early failures;
the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-2}.
%
\begin{figure}
\includegraphics[width=\textwidth]{fig6}
\caption{Sets of posterior predictive reliability functions for the four component types
for surprisingly early failures (case~2).}
\label{fig:comppost-2}
\end{figure}
%
Having observed the system only until $t = 2$, the data are not very informative,
such that prior and posterior predictive reliability bounds are very similar.
For C, the effect of the early failures is however still visible,
and posterior imprecision, i.e., the range between lower and upper posterior bound, is notably larger
as compared to prior imprecision, and substantially larger than posterior imprecision in case~1.
The effect for P is less pronounced,
mainly because observing $\vec{t}^\text{P} = (0.25, 0.5, 2^+, 2^+)$ for P is less extreme
as observing $\vec{t}^\text{C} = (1, 2, 2^+, 2^+)$ for C.

@@

For the third case, we assume to observe surprisingly late failures,
namely $t_1^\text{C} = 11$, $t_2^\text{C} = 12$, $t_1^\text{P} = 8$, $t_2^\text{P} = 9$,
and $\tnow = 12$ (so $t_1^\text{M} = t_1^\text{H} = t_3^\text{C} = t_4^\text{C} = t_3^\text{P} = t_4^\text{P} = 12^+$);
the corresponding posterior predictive component distributions are given in Figure~\ref{fig:comppost-3}.
%
\begin{figure}
\includegraphics[width=\textwidth]{fig7}
\caption{Sets of posterior predictive reliability functions for the four component types
for surprisingly late failures (case~3).}
\label{fig:comppost-3}
\end{figure}
%
Having observed the system for a much longer time than in case 2,
the data contain now much more information,
resulting in considerable differences between prior and posterior bounds. %predictive reliability
The effect of these surprisingly late failures is most prominent for P,
with a set considerably shifted to the right and having very wide posterior bounds.
The posterior set for C also indicates that,
after having seen these late failures, one expects type C components to fail much later.
This effect is also visible for M and H,
but is weaker for them as there is only one component of each in the system.
